Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-07 ms.tex
explain Kcmb to MJy/sr conversion factor

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a spectral index $\alpha$=$-1$ spectrum. The values of $u_{\nu_i, IRAS}$
are listed in the second column of \cite{planckresponse} Table 6. 
$u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor relative to
the \IRAS~convention for band $\nu_i$ and a MBB($T$, $\beta$) spectrum.
To reiterate, for $\nu_i$$\le$353 GHz $u_{\nu_i}(T_k, \beta_k)$ has units 
of (MJy/sr)/$K_{CMB}$, and therefore $I_{\nu_{i}}$ will have different 
units depending on the band $\nu_i$, though $I_{\nu_{i}}$ always has 
the same units as the native band $\nu_i$ map.

>>>>

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a power law specrum with spectral index $\alpha$=$-1$. The values of 
$u_{\nu_i, IRAS}$ are listed in the second column of \cite{planckresponse} 
Table 6. $u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor 
relative to the \IRAS~convention for band $\nu_i$, assuming a MBB($T$, $\beta$)
spectrum. In practice, we retrieve $u_{\nu_i}(T, \beta)$ in a fashion similar 
to that used for the $b_{\nu_i}(T, \beta)$ color corrections, using a set of 
precomputed one-dimensional look-up tables. To reiterate, for $\nu_i$$\le$353 
GHz $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and therefore 
$\tilde{I}_{\nu_{i}}$ will have different units depending on the band $\nu_i$, 
though $\tilde{I}_{\nu_{i}}$ always has the same units as the native band 
$\nu_i$ map.
